TUGAS POLINOMIAL CHAPTER 15

### 2021-10-12 Semester I/Pemrograman dalam Sains/Minggu VIII/pr.Rmd
tes

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.1"}
f = function(x){x^4 + 4*x^2 + 7}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.1"}
knitr::include_graphics("15_1.png")
```

>>>>

```{r,include=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.1"}
f = function(x){x^4 + 4*x^2 + 7}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@

```{r out.width = "100%",echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.1"}
knitr::include_graphics("15_1.png")
```
